Project Thesis/Report

### 2022-01-06 Gandhi_Project_Report/draft3.tex
Done working through all edits Ch1-Ch3

In this chapter, we discuss results pertaining to the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should have to avoid adding distortion to its state space representation, as well as then ensuring that the single-delay dynamics (SDD) are conjugate (or at least semi-conjugate to the system). 
The SDD can then be used to forecast and reconstruct the underlying attractor. \ednote{Is this attractor assumed to exist?}

@@

A nonautonomous dynamical system is simply a dynamical system (as defined before in \ref{Dfn_DS}) where the input $u$ from the input space $U$, a  topological space, is time-dependent.

We immediately recall the figure first defined in \ref{eqn_conjugacy} and remind ourselves of our ultimate goal to forecast the evolution of an unknown nonautonomous dynamical system $(U,T)$ by constructing a conjugate system such as $(V,S)$ below.

@@

To do this, the need arises to consider a driven dynamical system where input is taken from both an input space $U$, and an underlying state space $X$. 
This is done to account, in a manner more similar to the true scenario, for the influence of both the input and the actual state of the system at a specific timestep.

\begin{Definition}
  [\bf Driven and Compactly Driven Dynamical System] \label{Dfn_DDS}
A driven dynamical system comprises two topological metric spaces $U$, $X$ and a continuous function  $g:U\times{X}\to{X}$ where $g(u_n, x_n)=x_{n+1}$. 
The dynamics on X are generated by the update equation $x_{n+1}=g(u_n, x_n)$ where $n\in\mathbb{Z}$, input $u_n$ from $U$ and state $x_n$ belonging to $X$, where $X$ is compact. 
If the input space $U$ is compact, we refer to the system as compactly driven. 
Abbreviated, we shall refer only to the \emph{driven system $g$}, with all other entities being understood implicitly.
\end{Definition}

In particular, a nonautonomous dynamical system may be generated from $U$; any input $\overline{u}$, a bi-infinite sequence from $U$, gives rise to the sequence of self-maps $\{g(u_n, \cdot)\}_{n\in\mathbb{Z}}$ contained in $X$.
Physically, one may think of this bi-infinite sequence as referring to a system that has been running for an incredibly long period at the time of the first measurement taken from the system (alternatively, the first time a probe is inserted into the system to take an observation).

\begin{Definition}
  [\bf Entire Solution] \label{Dfn_Soln}
  A sequence $\{x_n\}_{n\in\mathbb{Z}}\subseteq{U}$ is called an entire solution(or simply a solution) to the driven system  $g$ with input $\overline{u}$ when it satisfies 
  \[g(u_{n-1}, x_{n-1})=x_n\] for all $n\in\mathbb{Z}$
\end{Definition}

It is important to emphasise that a sequence satisfying the update equation above can only be a solution if $x_n\in{U}$ for all $n\in\mathbb{Z}$. Consider the example below.

\begin{Example}\label{ex_halfux}
  The only solution  $\{x_n\}_{n\in\mathbb{Z}}$ to the driven system  $g(u,x)=\frac{ux}{2}$, where $X=[0,1]$, $U=[0,1]$,  is the zero solution $x_n\equiv0$.
  To see this, consider any $x_n=a\in[0,1]$ where $a\neq{0}$.  Let $\overline{u}\in{U}$ be an non-zero constant sequence , say $u_n=0.5$. 
  The driven system may be rewritten as $x_{n-1}=\frac{2x_n}{u_{n-1}}=4x_n$ and the  iterates of $x_n$ in backward time will increase by a factor of 4 at each timestep. 
  Thus for some $m\leq{n}$,  $1<x_m$ i.e. $x_m\notin{X}$. So ${\{x_n\}}_{n\in\mathbb{Z}}$ is not a solution and it follows that the only possible solution is the zero solution.
\end{Example}

@@

\begin{Example}\label{Ex_exp}
 Consider the driven system $g(u_n,x_n)=x^n$ for $X=[0,1]$, $U=\mathbb{R}$. The system has an uncountable number of solutions, as there exists a solution for every $x\in{X}$ which also passes through the point $x$ and $lim_{n\to\infty}x_n=0$, $lim_{n\to{-}\infty}x_n=1$. 
 The proof is deferred to immediately after the next paragraph.

@@

As the solutions to a driven system are often considered, we next identify a subspace $X_U$ of $X$ that contains all possible solutions. To realize such a subspace of a driven system $g$, the concept of a reachable set is defined.

@@

We note that $x\in{X_n(\overline{u})}$ if and only $g$ has a solution $\{x_k\}$ for $x_n=x$ and input $\overline{u}$. \textbf{Cite}.
This will lead to a result established later, but which is worth taking note of now: \textit{$g$ being a topological contraction is equivalent to the existence of a unique entire solution.} To this end we define the notion of a topological contraction.

\begin{Definition}
  [\bf Topological Contraction]\label{Dfn_TopContr}
  A function $g:U\times{X}\to{X}$ is a topological contraction if for all $n\in\mathbb{Z}$ and all $\overline{u}\subseteq{U}$, $X_n(\overline{u})$ is a singleton subset of X.  
\end{Definition}

@@

\begin{Theorem}\label{Thm_CompactExistence}
  If $X$ is compact then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
\begin{proof}
  Consider an input $\overline{u}={\{u_n\}}_{n\in\mathbb{Z}}\subseteq{U}$ and driven system $g:U\times{X}\to{X}$  generating a sequence ${\{x_n\}}_{n\in\mathbb{Z}}$ in the compact space $X$. 
  Since $X$ is a metric space, it follows immediately from a well-known result in Analysis (\textbf{Cite}) that $\{x_n\}$ has a convergent subsequence which then is a solution. 
\end{proof}

@@

One of the first result obtained upon defining the USP, is the fact that every solution will attract any different initial conditions towards the component parts of the solution, i.e. that the solution $\Psi$ is a non-autonomous uniform attractor. \ednote{Define Uniform Attractor before stating theorem.}

\begin{Theorem} \label{Thm_AttractorSoln}
  If $g$ has USP, then any solution to $g$ is a non-autonomous uniform attractor 
\end{Theorem}
\begin{proof}
  \cite{Manju_Nonlinearity}
\end{proof}

\ednote{Additional discussion on USP?} 
Having already defined the reachable set $X_U$, we pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

The question now becomes whether we may establish a conjugacy as presented below for $g$ driven

@@

Does such a function $h$ for the driven system defined above exist? If $g$ has the USP and $\Psi(u)=\{x_n\}_{n\in\mathbb{Z}}$ then $h$, defined by  $h(\cev{u}_n):=g(u_n,x_{n-1})=x_n$, will satisfy the semi-conjugacy in the graph above \ref{Scomm_h}.
Regrettably, the mapping $h$ is not guaranteed to exist in general.

Re-sketching the graph\ref{Scomm_h} above by fixing the input $v$ in $g$ and replacing $X_U$ by its left-infinite sequence space $\overleftarrow{U}$, we obtain the graph below. In this case, the function $H:\overleftarrow{U}\to\overleftarrow{X}_U$, a map that is both continuous and surjective, is called a \emph{causal mapping}. 
make special note of a 
\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

Note that even when $h$ does exist, we are not guaranteed its injectivity. Considering again example \ref{ex_halfux}, we see that even if $h$ were to exist, it could not be injective as $X_U=\{0\}$.

An embedding of the space $\overleftarrow{U}$   would allow one to establish topological conjugacy, which in turn provides stronger results than merely obtaining a coarse-grained representation via a causal mapping.

  Before formalising this, we make mention of the concept of the inverse-limit system of a dynamical system $(U,T)$. 
  In broad sweeps, the inverse-limit system of a dynamical system is a self-map on a subset of an infinite-dimensional space \textbf{(Expand)} where each point in the inverse-limit space corresponds to a backward orbit of the map $T$. In literature, the inverse-limit space is denoted by $\hat{U}_T\subseteq\overleftarrow{U}$ \cite{manjunath2021universal}. 
  The map $T$, then, induces a self-map $\hat{T}:\widehat{T}: (\ldots,u_{-2},u_{-1}) \mapsto  (\ldots,u_{-2},u_{-1},T(u_{-1}))$ on $\widehat{U}_T$

\begin{Definition}
  [\bf Causal Embedding]\label{Dfn_CausalEmbed}
  A driven system $g$ is said to causally embed the dynamical system $(U,T)$ if 
  \vspace{-8mm}
\begin{enumerate}[noitemsep, label=\roman*.]
  \item The diagram in \ref{SCausal_H} commutes (i.e. $g$ is a universal semi-conjugacy),
  \item $H_2(\overline{u}):=(h(r\overline{u}, h(\overline{u})))$ embeds the inverse-limit space $(\hat{U}, \hat{T})$ of $(U,T)$ in $X\times{X}$.
\end{enumerate}
\end{Definition}

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: If $H:\overleftarrow{U}\to\overleftarrow{X}_U$ is also injective (in addition to being surjective, and hence bijective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$ and we refer to $H$ as a \emph{causal embedding}.

@@

When g has the USP, the diagram below illustrates the operation of the the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is an observable as discussed in an above section (\ref{TakensEmbedding}).

\begin{figure}[ht]
  \includegraphics[scale=0.3]{actionofh_H.png}
  \centering
  \label{fig:actionh_H}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.4]{memloss_conttime.png}
  \centering
  \label{fig:memoryLosscont_time}
\caption{Approaching the true solution if g has the UAP}
\end{figure}

@@

\begin{figure}[ht] \label{Fig_Gamma}
  \includegraphics[scale=0.3]{gammatemp.png}
  \centering
  \label{fig:conjugacy_with_Gamma}
\end{figure}

>>>>

In this chapter, we discuss results pertaining to the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should have to avoid adding distortion to its state space representation. We then describe its \emph{single-delay dynamics} (SDD) and then recall conditions on the driven system so that the SDD is conjugate (or at least semi-conjugate) to the underlying system. 
The SDD can then be used to forecast and reconstruct the underlying system. \ednote{Is this attractor assumed to exist? M:  I replaced  it with the system. Attractor is also a commonly used terminology since we observe data from an attractor in almost all cases.}

@@

A nonautonomous dynamical system is simply a dynamical system (as defined before in \ref{Dfn_DS}) \ednote{M:I am not sure where it was defined before. If not, please say, A NDS comprises a family of map $\{g_n\}_{n \in \mathbb{Z}}$ and say  each $g_n$ could arise as a consequence of an input $u_n$.} from the input space $U$, a  topological space, is time-dependent.

We immediately recall the figure first defined in \ref{eqn_conjugacy}  \ednote{Please use eqref instead of ref while cross-citing equations} and remind ourselves of our ultimate goal to forecast the evolution of an unknown nonautonomous dynamical system $(U,T)$ \ednote{We are not forecasting a nonautonomous, but an autonomous system} by constructing a conjugate system such as $(V,S)$ below. \ednote{M: Maybe something like this sounds better: We learn a system that is conjugate to an underlying or unknown dynamical system by using the measurements from  the unknown system.}

@@

To find a $\phi$ \ednote{M: Have edited here}, the need arises to consider a driven dynamical system where input is taken from an input space $U$, and the state of a space $X$ is updated. 
This is done to account, in a manner more similar to the true scenario, for the influence of both the input and the actual state of the system at a specific time-step. \ednote{M : I understand this sentence, but am not sure if a general audience would. So please elaborate the sentence or omit}

\begin{Definition}
  [\bf Driven and Compactly Driven Dynamical System] \label{Dfn_DDS} \rm
A driven dynamical system comprises two topological metric spaces $U$, $X$ and a continuous function  $g:U\times{X}\to{X}$ where $g(u_n, x_n)=x_{n+1}$. 
The dynamics on X are generated by the update equation $x_{n+1}=g(u_n, x_n)$ where $n\in\mathbb{Z}$, input $u_n$ from $U$ and state $x_n$ belonging to $X$, where $X$ is compact.  \ednote{M : The sentence ``The dynamics on X are generated by ..." does not define anything, so mathematicians do not include it as part of a definition, and can be moved after the definition.}
If the input space $U$ is compact, we refer to the system as compactly driven. 
Abbreviated, we shall refer only to the \emph{driven system $g$}, with all other entities being understood implicitly.
\end{Definition}

In particular, a nonautonomous dynamical system may be generated from $U$; any input $\overline{u}$, a bi-infinite sequence from $U$, gives rise to the sequence of self-maps $\{g(u_n, \cdot)\}_{n\in\mathbb{Z}}$ contained in $X$.
Physically, one may think of this bi-infinite sequence as referring to a system that has been running for an incredibly long period at the time of the first measurement taken from the system (alternatively, the first time a probe is inserted into the system to take an observation) \ednote{Time is a label we put. We can label the first sample as $0$th or $-10000$th. So the word incredibly is not necessary, all we need is good amount of data.}

\begin{Definition}
  [\bf Entire Solution] \label{Dfn_Soln}
  A sequence $\{x_n\}_{n\in\mathbb{Z}}\subset X$ \ednote{Please avoid subseteq as it is ambiguous} is called an entire solution(or simply a solution) of the driven system  $g$ with input $\overline{u}$ when it satisfies 
  \[g(u_{n-1}, x_{n-1})=x_n\] for all $n\in\mathbb{Z}$
\end{Definition}

It is important to emphasise that a sequence $\{x_n\}$ satisfying the update equation above can only be a solution if $x_n\in{U}$ holds for all $n\in\mathbb{Z}$ and just for $n>0$. Consider the example below.

\ednote{M: Only theorems, lemmas and propositions are in italics. For Definitions, remarks and examples, please add slash-rm command to keep it in normal mode}

\begin{Example} \rm \label{ex_halfux}
  The only solution  $\{x_n\}_{n\in\mathbb{Z}}$ to the driven system  $g(u,x)=\frac{ux}{2}$, where $X=[0,1]$, $U=[0,1]$,  is the zero solution $x_n\equiv0$.
  To see this, consider any $x_n=a\in[0,1]$ where $a\neq{0}$.  Let $\overline{u}\in{U}$ be an non-zero constant sequence , say $u_n=0.5$. 
  The driven system may be rewritten as $x_{n-1}=\frac{2x_n}{u_{n-1}}=4x_n$ and the  iterates of $x_n$ in backward time will increase by a factor of 4 at each timestep. 
  Thus for some $m\leq{n}$,  $1<x_m$ i.e. $x_m\notin{X}$. So ${\{x_n\}}_{n\in\mathbb{Z}}$ is not a solution and it follows that the only possible solution is the zero solution.
\end{Example}
\ednote{Nicely written!}

@@

\begin{Example}\label{Ex_exp} \rm 
 Consider the driven system $g(u_n,x_n)=x^n$ for $X=[0,1]$, $U=\mathbb{R}$. The system has an uncountable number of solutions, as there exists a solution for every $x\in{X}$ which also passes through the point $x$ and $lim_{n\to\infty}x_n=0$, $lim_{n\to{-}\infty}x_n=1$. 
 The proof is deferred to immediately after the next paragraph. \ednote{Make the proof a remark and please cite the remark}

@@

As the solutions to a driven system are often considered to be an important entity \cite{M: edited the sentence here}, we next identify a subspace $X_U$ of $X$ that contains all possible solutions. To realize such a subspace of a driven system $g$, the concept of a reachable set is defined.

@@

We note that $x\in{X_n(\overline{u})}$ if and only $g$ has a solution $\{x_k\}$ for $x_n=x$ and input $\overline{u}$. \textbf{Cite}.
This will lead to a result established later, but which is worth taking note of now: \textit{$g$ being a topological contraction is equivalent to the existence of a unique entire solution.} To this end we define the notion of a topological contraction. \ednote{I do not think you need the definition of a topological contraction unless it is defined through a process. Please note that you have defined $X_n(\bar{u})$ differently than what was in the earlier works. Now it is just the collection of solution values at time $n$ with the input $\bar{u}$ and topological contraction is just paraphrasing the USP definition.}

\begin{Definition}
  [\bf Topological Contraction]\label{Dfn_TopContr}
  A function $g:U\times{X}\to{X}$ is a topological contraction if for all $n\in\mathbb{Z}$ and all $\overline{u}\subseteq{U}$, $X_n(\overline{u})$ is a singleton subset of $X$.  
\end{Definition}

@@

\begin{Theorem}\label{Thm_CompactExistence}
 Let $g$ be a driven system.  If $X$ is compact then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
\begin{proof}
  Consider an input $\overline{u}={\{u_n\}}_{n\in\mathbb{Z}}\subseteq{U}$ and driven system $g:U\times{X}\to{X}$  generating a sequence ${\{x_n\}}_{n\in\mathbb{Z}}$ in the compact space $X$ \ednote{This statement is not correct.}. 
  Since $X$ is a metric space, it follows immediately from a well-known result in Analysis (\textbf{Cite}) that $\{x_n\}$ has a convergent subsequence which then is a solution.  \ednote{This is not a valid proof. Please refer to the proof existence of a solution in \cite{Manju_ESP}.}
\end{proof}

@@

One of the first result obtained upon defining the USP, is the fact that every solution will attract any different initial conditions towards the component parts of the solution, i.e. that the solution $\Psi$ is a non-autonomous uniform attractor. \ednote{Define Uniform Attractor before stating theorem or else omit the statement.}

\begin{Theorem} \label{Thm_AttractorSoln}
  If $g$ has USP, then any solution to $g$ is a non-autonomous uniform attractor 
\end{Theorem}
\begin{proof}
\ednote{M: You can omit the theorem, and just say it is a uniform attractor in the nonautonomous dynamical systems literature \cite{Manju_Nonlinearity}, and say the discussion on nonautonomous attractors is beyond the scope of the thesis.}

\end{proof}

\ednote{Additional discussion on USP? M: Please do so by stating that it is equivalent to the echos state property. See the paper with Adriaan and paraphrase} 
Having already defined the reachable set $X_U$, we pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

The question now becomes whether we may establish a semi-conjugacy \ednote{M: I have changed it to a semi-conjugacy since conjugacy amounts to asking a infinite-dimensional space $\overleftarrow{U}$ to be embedded in $X_U$ which is not possible. } as presented below for the driven system $g$.

@@

Does such a function $h$ for the driven system defined above exist? If $g$ has the USP and $\Psi(u)=\{x_n\}_{n\in\mathbb{Z}}$ then $h$, defined by  $h(\cev{u}_n):=g(u_n,x_{n-1})=x_n$, will satisfy the semi-conjugacy in the graph above \ref{Scomm_h}.
Regrettably, such a continuous mapping $h$ is not guaranteed to exist \cite{M: Have edited here} when $g$ does not have the USP \cite[Lemma 5]{Manju_Nonlinearity}.

Re-sketching the commutativity diagram \ref{Scomm_h} above by fixing the input $v$ in $g$ and replacing $X_U$ by its left-infinite sequence space $\overleftarrow{U}$, we obtain the diagram below. In this case, the function $H:\overleftarrow{U}\to\overleftarrow{X}_U$, a map that is both continuous and surjective, is called a \emph{causal mapping}. 
make special note of a \ednote{something you want to fill?} 
\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

Note that even when $h$ does exist, we are not guaranteed its injectivity. Considering again example \ref{ex_halfux}, we see that even if $h$ were to exist, it could not be injective as $X_U=\{0\}$ \ednote{M: I feel these two sentences should be made after the definition of $h$ rather than here}.

An embedding of the space $\overleftarrow{U}$   \ednote{M: in which space? is it the inver-limit space instead?} would allow one to establish topological conjugacy, which in turn provides stronger results than merely obtaining a coarse-grained representation via a causal mapping \cite{M: I feel this is very confusing to the reader as the co-domain of causal mapping is the left-infinite space and , so please omit if possible. You can just say we want to restrict inputs to the left-infinite orbits of a dynamical system and then explore conjugacy instead of a mere semi-conjugacy}.

Before formalising this, we make mention of the concept of the inverse-limit system of a dynamical system $(U,T)$. 
  In broad sweeps, the inverse-limit system of a dynamical system is a self-map on a subset of an infinite-dimensional space \textbf{(Expand)} where each point in the inverse-limit space corresponds to a backward orbit of the map $T$. Following \cite{manjunath2021universal}, the inverse-limit space is denoted by $\widehat{U}_T\subset \overleftarrow{U}$, and defined as $\widehat{U}_T\subset: = \{ (\ldots,u_{-2},u_{-1}): Tu_{i} = u_{i+1}$. 
  The map $T$, then, induces a self-map $\widehat{T}: (\ldots,u_{-2},u_{-1}) \mapsto  (\ldots,u_{-2},u_{-1},T(u_{-1}))$ on $\widehat{U}_T$.

\begin{Definition}
  [\bf Causal Embedding]\label{Dfn_CausalEmbed}
  A driven system $g$ is said to causally embed the dynamical system $(U,T)$ if 
  \vspace{-8mm}
\begin{enumerate}[noitemsep, label=\roman*.]
  \item The diagram in \ref{SCausal_H} \ednote{M: It is actually Eqn. 1.1 and not 1.2}commutes (i.e. $h$ is a universal semi-conjugacy) ,
  \item $H_2(\overline{u}):=(h(r\overline{u}, h(\overline{u})))$ embeds the inverse-limit space $(\widehat{U}, \hat{T})$ of $(U,T)$ in $X\times{X}$ \ednote{M: Please replace $\widehat{U}$ by $\widehat{U}_T$ here and throughout}.
\end{enumerate}
\end{Definition}

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: If $H:\overleftarrow{U}\to\overleftarrow{X}_U$ is also injective (in addition to being surjective, and hence bijective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$ and we refer to $H$ as a \emph{causal embedding} \ednote{M : Causal embedding a dynamical system is different from the definition of causal embedding, so please edit/delete this paragraph and the next theorem and also in the remaining part till Section 1.2}.

@@

When $g$ has the USP, the diagram below illustrates the operation of the the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is an observable as discussed in an above section (\ref{TakensEmbedding}).

\begin{figure}[ht]
  %\includegraphics[scale=0.3]{actionofh_H.png}
  \centering
  \label{fig:actionh_H}
\end{figure}

@@

\begin{figure}[ht]
  %\includegraphics[scale=0.4]{memloss_conttime.png}
  \centering
  \label{fig:memoryLosscont_time}
\caption{Approaching the true solution if g has the UAP}
\end{figure}

@@

\begin{figure}[ht] \label{Fig_Gamma}
  % \includegraphics[scale=0.3]{gammatemp.png}
  \centering
  \label{fig:conjugacy_with_Gamma}
\end{figure}
